Manifold Clustering for Latent Structure Block Models

### 2022-02-23 draft/draft.Rmd
another animation

```{r, cache = TRUE}
maxit <- 50
animate <- TRUE
animation.dir <- '~/dev/manifold-block-models/draft'
random.starts <- 2
eps <- 1e-3
out <- lapply(seq(random.starts), function(i) {
  set.seed(i)
  intercept <- (i / random.starts > .5 + eps)
  manifold.clustering(Xhat, 2, 
                      parallel = TRUE, 
                      intercept = intercept, 
                      maxit = maxit,
                      eps = 1e-3,
                      verbose = FALSE,
                      animate = animate,
                      animation.dir = animation.dir,
                      animation.title = i)
})
names(out) <- paste('random', seq(random.starts))
names(out) <- sapply(seq(random.starts), function(i) {
  if (i / random.starts < .5 + eps) {
    paste('random', i, '\n(w/o intercept)')
  } else {
    paste('random', i, '\n(w/ intercept)')
  }
})

>>>>

```{r, cache = TRUE}
maxit <- 50
# animate <- TRUE
animation.dir <- '~/dev/manifold-block-models/draft'
random.starts <- 2
eps <- 1e-3
out <- lapply(seq(random.starts), function(i) {
  set.seed(i)
  intercept <- (i / random.starts > .5 + eps)
  manifold.clustering(Xhat, 2, 
                      parallel = TRUE, 
                      intercept = intercept, 
                      maxit = maxit,
                      eps = 1e-3,
                      verbose = FALSE,
                      animate = animate,
                      animation.dir = animation.dir,
                      animation.title = i)
})
names(out) <- paste('random', seq(random.starts))
names(out) <- sapply(seq(random.starts), function(i) {
  if (i / random.starts < .5 + eps) {
    paste('random', i, '\n(w/o intercept)')
  } else {
    paste('random', i, '\n(w/ intercept)')
  }
})
